Component response rate variation underlies the stability of highly complex finite systems

### 2020-03-26 notebook/ms.Rmd
Remove numbers on equations that are not referenced in the text

---
title: "Component response rate variation underlies the stability of highly complex finite systems"
author: "A. Bradley Duthie    ( alexander.duthie@stir.ac.uk )"
date: Biological and Environmental Sciences, University of Stirling, Stirling, UK,
  FK9 4LA
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - nature.csl
    reference_docx: docx_template.docx
bibliography: references.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage[utf8]{inputenc}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
link-citations: yes
linkcolor: blue
csl: nature.csl
biblio-style: apalike
---

@@

\begin{equation} \label{var_reduced}
\sigma^{2}_{M} = \sigma^{2}_{A}(1 + \sigma^{2}_{\gamma}).
\end{equation}

@@

\begin{equation} \label{rho_stab}
\Re(\lambda_{max}) \approx \sigma_{M}\sqrt{SC}\left(1 + \rho\right).
\end{equation}

>>>>

---
title: "Component response rate variation underlies the stability of highly complex finite systems"
author: "A. Bradley Duthie    ( alexander.duthie@stir.ac.uk )"
date: Biological and Environmental Sciences, University of Stirling, Stirling, UK,
  FK9 4LA
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - nature.csl
    reference_docx: docx_template.docx
bibliography: references.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage[utf8]{inputenc}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
link-citations: yes
linkcolor: blue
csl: nature.csl
biblio-style: apalike
---

@@

\begin{equation} 
\sigma^{2}_{M} = \sigma^{2}_{A}(1 + \sigma^{2}_{\gamma}). \nonumber
\end{equation}

@@

\begin{equation} 
\Re(\lambda_{max}) \approx \sigma_{M}\sqrt{SC}\left(1 + \rho\right). \nonumber
\end{equation}
